### 2023-09-22 sections/teaching.tex
LPPL v1.3c
Update teaching.tex

\begin{itemize}
\item{\small School of Business, {\bfseries Universidad Mayor}, Santiago, Chile}
\begin{itemize}
\item[$\circ$]{\small Machine Learning in Public Policy and Economics (workshop, Prof. Carla Cisternas), spring 2021}
\end{itemize}
\item{\small Department of Politics and International Relations, {\bfseries University of Oxford}, Oxford, UK}
\begin{itemize}
\item[$\circ$]{\small Comparative Government (undergraduate tutorial, Prof. Petra Schleiter), Hilary 2020}
\end{itemize}
\item{\small Faculty of Adminstration and Economics, {\bfseries Universidad de Santiago}, Santiago, Chile}
\begin{itemize}
\item[$\circ$]{\small Political Science I (undergraduate lecture), spring 2014, 2018, fall 2015-2019}
\item[$\circ$]{\small Political Science II (undergraduate lecture), spring 2015-2018}
\item[$\circ$]{\small Econometrics for Public Policies (undergraduate lecture), fall 2018}
\item[$\circ$]{\small Workshop for Research Design (graduate seminar), spring 2017-2018}
\item[$\circ$]{\small Research Methodology (undergraduate lecture), spring 2014-2015, fall 2015-2017}
\item[$\circ$]{\small Introduction to Quantitative Methods (undergraduate lecture), fall 2017}
\end{itemize}
\item{\small School of Government and Public Management, {\bfseries Universidad de Chile}, Santiago, Chile}
\begin{itemize}
\item[$\circ$]{\small Study of Political Phenomena (undergraduate lecture), fall 2016}
\item[$\circ$]{\small Political Analysis (undergraduate lecture), fall 2014}
\item[$\circ$]{\small Elite Theory and Democracy (undergraduate lecture, Prof. Alejandro Olivares), spring 2013-2014}
\end{itemize}
\end{itemize}

>>>>

\begin{itemize}
\item{\small School of Business, {\bfseries Universidad Mayor}, Santiago, CHL}
\begin{itemize}
\item[$\circ$]{\small Machine Learning in Public Policy and Economics (workshop, Prof. Carla Cisternas), spring 2021}
\end{itemize}
\item{\small Department of Politics and International Relations, {\bfseries University of Oxford}, Oxford, GBR}
\begin{itemize}
\item[$\circ$]{\small Comparative Government (undergraduate tutorial, Prof. Petra Schleiter), Hilary 2020}
\end{itemize}
\item{\small Faculty of Adminstration and Economics, {\bfseries Universidad de Santiago}, Santiago, CHL}
\begin{itemize}
\item[$\circ$]{\small Political Science I (undergraduate lecture), spring 2014, 2018, fall 2015-2019}
\item[$\circ$]{\small Political Science II (undergraduate lecture), spring 2015-2018}
\item[$\circ$]{\small Econometrics for Public Policies (undergraduate lecture), fall 2018}
\item[$\circ$]{\small Workshop for Research Design (graduate seminar), spring 2017-2018}
\item[$\circ$]{\small Research Methodology (undergraduate lecture), spring 2014-2015, fall 2015-2017}
\item[$\circ$]{\small Introduction to Quantitative Methods (undergraduate lecture), fall 2017}
\end{itemize}
\item{\small School of Government and Public Management, {\bfseries Universidad de Chile}, Santiago, CHL}
\begin{itemize}
\item[$\circ$]{\small Study of Political Phenomena (undergraduate lecture), fall 2016}
\item[$\circ$]{\small Political Analysis (undergraduate lecture), fall 2014}
\item[$\circ$]{\small Elite Theory and Democracy (undergraduate lecture, Prof. Alejandro Olivares), spring 2013-2014}
\end{itemize}
\end{itemize}
